\cvline{08.2014 - 06.2019}{
\en{
\large{Norwegian University of Science and Technology, individual courses}
% main content - En
\newline
Management, psychology, and IT.
}\no{
\large{Norges Teknisk-Naturvitenskapelige Universitet, individuelle studier}
% Hovedinnold - No
\newline
Ledelse, psykologi, og IT.
}}
%%-----------------------------------------------------------------------------

\cvline{08.2012 - 06.2014}{
\en{
\large{NTNU, master in computer science}
% main content - En
\newline
Thesis in \textit{Artificial Intelligence} and \textit{Data and Information
Management}; '\textit{Tweet Sentiment, Sentiment Trend, and a Comparison with
Financial Trend Indicators.}'
}\no{
\large{NTNU, master informatikk}
% Hovedinnold - No
\newline
Masteroppgave innen \textit{Data- og informasjonsforvaltning}; '\textit{Tweet Sentiment, Sentiment Trend, and a Comparison
with Financial Trend Indicators.}'
}}
%%-----------------------------------------------------------------------------

\cvline{08.2009 - 06.2012}{
\en{
\large{NTNU, bachelor in computer science}
% main content - En
\newline
System development and artificial intelligence have been in focus during the
degree. The results of the bachelor thesis, \textit{Role-based Quality of
Service for Web
Services}, was
published by FFI(Norwegian Defence Research Establishment) in \textit{Globecom
Workshops}.
}\no{
\large{NTNU, bachelor informatikk}
% Hovedinnold - No
\newline
Systemutvikling og kunstig intelligens har vært mine fokusområder under
bachelorgraden. 
Resultatene fra bacheloroppgaven, \textit{Role-based Quality of Service for Web
Services}, er publisert av Forsvarets
Forskningsinstitutt i \textit{Globecom Workshops}.
}}
%%-----------------------------------------------------------------------------

\cvline{08.2006 - 06.2009}{
\en{
\large{Greveskogen high school, Tønsberg}
% main content - En
\newline
Focus on math, physics and IT.
}\no{
\large{Greveskogen Vidregående Skole, Tønsberg}
% Hovedinnold - No
\newline
Fokus på matte, fysikk og IT.
}}
%%-----------------------------------------------------------------------------

%\cvline{08.2003 - 06.2006}{
%\en{
%\large{Preseterød Secondary School, Tønsberg}
%% main content - En
%}\no{
%\large{Presterød Ungdomskole, Tøsnberg} 
%}
%% Hovedinnold - No
%}}
%%-----------------------------------------------------------------------------
