
\cvline{09.2020 - current}{
\en{
\larger{\textbf{Dfind Direction}. \textit{Chief Consultant}}
% main content - En
\newline
Dfind Direction is the place for highly skilled business minded tech
consultants, managers, and architects. We help you set a course, stay on it, and
finish the project.
\newline
- Cloud Developer at The Future Group
\newline
- Java \& Payment developer at Norwegian Air Shuttle
\newline
}
\no{
\larger{\textbf{Capgemini}. \textit{Senior Konsulent}}
% Hovedinnold - No
\newline
Sjefskonsulent
\newline
}
% tags
\en{\textit{Tags: }}
\no{\textit{Merkelapper: }}
CloudFoundry, DevOps, Azure, PowerShell, Jira, Concourse
}
%%-----------------------------------------------------------------------------

\cvline{04.2020 - 09.2020}{
\en{ 
\larger{\textbf{Capgemini}. \textit{Senior Consultant}}
% main content - En
\newline
Working on the Difa/Eik project to create the new dataplatform for the
pharmacies in Norway. Worked on the platform team, mainly trying to improve
CI/CD and doing backlog grooming. 
\newline
}
\no{
\larger{\textbf{Capgemini}. \textit{Senior Konsulent}}
% Hovedinnold - No
\newline
Senior Konsulent
\newline
}
% tags
\en{\textit{Tags: }}
\no{\textit{Merkelapper: }}
CloudFoundry, DevOps, Azure, PowerShell, Jira, Concourse
}
%%-----------------------------------------------------------------------------

\cvline{04.2020 - 04.2020}{
\en{
\larger{\textbf{Solidify}. \textit{DevOps Specialist}}
% main content - En
\newline
I would have started the local office of Solidify in Oslo, Norway. But due to Covid-19
this did not happen. 
\newline
}
\no{
\larger{\textbf{Solidify}. \textit{DevOps Specialist}}
% Hovedinnold - No
\newline
Senior Konsulent
\newline
}
% tags
\en{\textit{Tags: }}
\no{\textit{Merkelapper: }}
DevOps, GitHub, Azure, Management, Leadership
}
%%-----------------------------------------------------------------------------

\cvline{04.2018 - 03.2020}{
\en{
\larger{\textbf{Dfind Consulting}. \textit{Senior Consultant}}
% main content - En
\newline
Magical potato that solves problems across the full range of any IT stack.
Evolving leadership and seniority. Exploring solutions and technology.
Because good experiences and team spirit is imperative to outstanding
deliveries.
\newline
- DevOps and Fullstack Engineer at Gjensidige
\newline
\textit{Tags:}
Windows(Server 2012R2, 10), DevOps, PowerShell, Jenkins, Team lead
}\no{
\larger{\textbf{Dfind Consulting}. \textit{Senior Konsulent}}
% Hovedinnold - No
\newline
Senior Konsulent
\newline
\textit{Merkelapper:}
Windows(Server 2012R2, 10), DevOps, PowerShell, Jenkins, Team lead
}}
%%-----------------------------------------------------------------------------

\cvline{05.2015 - 03.2018}{
\en{
\larger{\textbf{Netlight AS}. \textit{IT Consultant}}
% main content - En
\newline
Fullstack developer. Providing business value and cheerful smiles to clients
every day!
Organizing meetups, and an internal conference on a volunteer basis.
\newline
- Fullstack at Reisegiganten AS. 
\newline
- Fullstack at Schibsted Products and Technoloy
\newline
- Fullstack at Kudos
\newline
- Fullstack at Sparebanken 1
\newline
\textit{Tags:}
Perl, Java, Javascript, Angular.js, D3.js, AWS, Linux, Deops, Infrastructure,
React.js, 
}\no{
\larger{\textbf{Netlight AS}. \textit{IT Konsulent}}
% Hovedinnold - No
\newline
Fullstack utvikler.
\newline
\textit{Merkelapper:}
Perl, Java, Javascript, SOLR, AWS, Cloud, Infrastruktur, Linux, DevOps, 
}}
%%-----------------------------------------------------------------------------

\cvline{08.2014 - 12.2014}{
\en{
\larger{\textbf{Næringslivsnettverket KiD}. \textit{System Developer}}
% main content - En
\newline
System development of \url{http://kid.item.ntnu.no/}
\newline
\textit{Technologies:}
Java, Play framework, Knockout.js
}\no{
\larger{\textbf{Næringslivsnettverket KiD}. \textit{Systemutvikler}}
% Hovedinnold - No
\newline
Utvikling av \url{http://kid.item.ntnu.no/}
\newline
\textit{Teknologier:}
Java, Play-rammeverket, Knockout.js
}}
%%-----------------------------------------------------------------------------

\cvline{12.2012 - 11.2013}{
\en{
\larger{\textbf{Academic Work}. \textit{Consultant} on assignment to
\textit{Coperiosenteret AS}}
% main content - En
\newline
System administration, setup of a new website, and general computer support.
\newline
\textit{Technologies:}
Joomla, PHP, HTML5, CSS3
}\no{
\larger{\textbf{Academic Work}. \textit{Konsulent} på oppdrag hos
\textit{Coperiosenteret AS}}
% Hovedinnold - No
\newline
Systemadministrasjon, oppsett av ny nettside, generell IT-support.
\newline
\textit{Teknologier:}
Joomla, PHP, HTML5, CSS3
}}
%%-----------------------------------------------------------------------------

\cvline{06.2012 - 08.2012}{
\en{
\larger{\textbf{iNic AS}. \textit{System developer}}
% main content - En
\newline
Work on a webservice for registering domain names. Setup of Git server for
internal use. Systems setup and administrations.
\newline
\textit{Technologies:} 
Perl, Git, Server Administration, Ubuntu Server
}\no{
\larger{\textbf{iNic AS}. \textit{Systemutvikler}}
% Hovedinnold - No
\newline
Arbeid med webservice for registrering av domener. Intern Git server.
Systemadministrasjon.
\newline
\textit{Teknologier:}         
Perl, Git, Systemadministrasjon, Ubuntu Server
}}
%%-----------------------------------------------------------------------------

\cvline{06.2010 - 08.2010}{
\en{
\larger{\textbf{Proffcom}. \textit{Customer Service Consultant}}
% main content - En
}\no{
\larger{\textbf{Proffcom}. \textit{Kundeservice, telefon}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------

\cvline{07.2006}{
\en{
\larger{\textbf{ADR}. \textit{Summer Assistant}}
% main content - En
}\no{
\larger{\textbf{ADR}. \textit{Sommerassistent}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------
