
\cvline{08.2016 - current}{
\en{
\larger{\textbf{Polar Interesseorganisasjon}. \textit{Volunteer}}
% main content - En
\newline 
Organizing LAN parties in Vestfold, Norway.
\newline
2021 - Stab \& Tech; 2020-2017 - Tech; 2016 - Security;
}\no{
\larger{\textbf{Polar Interesseorganisasjon}. \textit{Frivillig}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------

\cvline{12.2015 - 04.2020}{
\en{
\larger{\textbf{The Gathering}. \textit{Crew member; Tech:Nett|Server}}
% main content - En
\newline
Network and Server administration at The Gathering (www.gathering.org) - one of
the largest LAN parties in the world.
}\no{
\larger{\textbf{The Gathering}. \textit{Crewmedlem; Tech:Nett|Server}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------

\cvline{09.2014}{
\en{
\larger{\textbf{JavaZone}. \textit{Volunteer}}
% main content - En
}\no{
\larger{\textbf{JavaZone}. \textit{Frivillig}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------

\cvline{01.2013 - 12.2014}{
\en{
\larger{\textbf{Samfundets Interne Teater}. \textit{Backdrop builder}}
% main content - En
}\no{
\larger{\textbf{Samfundets Interne Teater}. \textit{Kulissebygger}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------

\cvline{06.2013 - 06.2014}{
\en{
\larger{\textbf{Studentmediene i Trondheim AS}. \textit{Manager of IT}}
% main content - En
\newline
Supervising the IT-budget, IT-strategy, projects and activity in relation to the
IT department. Improve skills in leadership, communication, project management,
system administration, and programming.
\newline
\textit{Projects:} Rebuilding the IT department. Development of a transaction
management system.
}\no{
\larger{\textbf{Studentmediene i Trondheim AS}. \textit{IT-sjef}}
% Hovedinnold - No
\newline
Budsjettansvar, IT-strategi, ansvar for IT-systemer og utvikling av disse.
Forbedrede kunnskaper innenfor ledelse, kommunikasjon, systemadministrasjon, og
programmering.
\newline
\textit{Prosjekter:}
Gjenoppbyggin av IT-avdelingen. Utvikling av et Transaksjonshåndteringssystem.
}}
%%-----------------------------------------------------------------------------

\cvline{01.2010 - 06.2013}{
\en{
\larger{\textbf{Under Dusken}:
\textit{Maskinist (manager of IT)},
\textit{system developer},
\textit{internal area responsible}
}
% main content - En
\newline
Responsible for IT systems and development. Improved skills in leadership, communication, team
work, and economy. 
\newline
\textit{Technologies:} Ubuntu server, Java, Spring, HTML, CSS
\newline
\textit{Projects:} Aranea, Pegadi
}\no{
\larger{\textbf{Under Dusken}:
\textit{Maskinist (IT-sjef)},
\textit{systemutvikler},
\textit{internområdeansvarlig}
}
% Hovedinnold - No
\newline
Ansvarlig for IT-systemer og utvikling av disse. Forbedrede kunnskaper innen
ledelse, kommunikasjon, team-arbeid, og økonomi. 
\newline
\textit{Teknologier:} Ubuntu server, Java, Spring, HTML, CSS
\newline
\textit{Prosjekter:} Aranea, Pegadi
}}
%%-----------------------------------------------------------------------------

\cvline{07.2010 \& 07.2011}{
\en{
\larger{\textbf{Slottsfjell festival}. \textit{Volunteer}}
% main content - En
}\no{
\larger{\textbf{Slottsfjell-festivalen}. \textit{Frivillig}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------

\cvline{08.2008 - 06.2009}{
\en{
\larger{\textbf{Tønsberg Ju Jitsu Club}. \textit{Instructor}}
% main content - En
}\no{
\larger{\textbf{Tønsberg Ju Jitsu Klubb}. \textit{Instruktør}}
% Hovedinnold - No
}}
%%-----------------------------------------------------------------------------
