\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}

% Set your name here
\def\name{Magnus Løken Kirø}

\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {IT, computer, science, computer science, cv},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.7in},
  left=1.0in,
  top=0.5in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.2em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.1in}

\begin{minipage}{0.35\linewidth}
  \href{http://www.link.no/}{} \\
  Postboks 146 \\
  3166 Tolvsrød\\
  Norway
\end{minipage}
\begin{minipage}{0.35\linewidth}
  \begin{tabular}{ll}
    Phone: & (+47) 91748566 \\
    Email: & \href{mailto:magnuskiro@gmail.com}{\tt magnuskiro@gmail.com} \\
	Born: & 15.03.1990\\
    Homepage: & \href{http://magnuskiro.no}{magnuskiro.no} \\
  \end{tabular}
\end{minipage}

\section*{Personal Profile}
\begin{itemize} 
	\item Currently my main occupation is my master thesis. The remainder of my
time is spent with the student media in Trondheim or brewing beer.  
I have strong interests in science, technology, and computers. 

	%\item I am currently studying computer science. Focusing on system design and development. My interests in computers are a key element to my work in the Student Newspaper and my personal life. I feel capable and ready to accept new challenges. 
\end{itemize}

% Start education. 
\section*{Education and Qualifications}
\begin{itemize} 
  \item[08.2012 - 06.2014 :] NTNU – Master in Computer Science. \\ 
Thesis in \textit{Artificial Intelligence} and \textit{Data and Information
Management}.  

  \item[08.2009 - 06.2012 :] NTNU – Bachelor in Computer Science.	

  \item[08.2006 - 06.2009 :] Greveskogen high school, Tønsberg. 
		Focus on math, physics and IT. 

  \item[08.2003 - 06.2006 :] Presterød Ungdomskole, secondary school.  
\end{itemize}

% Start Experience.
\section*{Experience \tiny{(Organization, \textit{possition)}}} 
\begin{itemize}

\item[06.2013 - 06.2014 :] Studentmediene i Trondheim AS, \textit{Manager of IT} \\
Supervising budgets, strategy, projects and activity in relation to the IT department. 
\\\textit{Skills improved:} Leadership, Communication, System Administration,
Programming

\item[12.2012 - 11.2013 :] Academic Work, \textit{Consultant} on assignment to \textit{Coperiosenteret AS} \\ 
System administration, setup of a new website, and general computer support.  
\\\textit{Skills improved:} Joomla, PHP, HTML5, CSS3

\item[06.2012 - 08.2012 :] iNic AS, \textit{System developer} \\
Work on a webservice for registering domain names. 
Setup of Git server for internal use.  
System setup and administration.
\\\textit{Skills improved:} Perl, Git, Server Administration, Ubuntu Server

\item[01.2010 - 06.2012 :] Under Dusken (the student newspaper of Trondheim),
\textit{Maskinist(Manager of IT)} \\
Responsible for IT systems and development. 
\\\textit{Skills improved:} Communication, Team Work, Ubuntu server,
Java, Spring, HTML, CSS. 

\item[06.2010 - 08.2011 :] Slottsfjell-festivalen, \textit{Volunteer},
development and hosting of an internal website.

\item[06.2010 - 08.2010 :] Proffcom, \textit{Customer Service Consultant}

\item[08.2007 - 06.2009 :] Tønsberg Ju Jitsu club, \textit{Instructor}

\item[07.2006 - 07.2006 :] ADR, \textit{Summer Assistant}

% END work experience. 
\end{itemize}

% Publications
\section*{Publications}
\begin{itemize}

%\item Role-based Quality of Service for Web Services, Frank T. Johnsen, Trude H.
%Bloebaum, Jørgen Nordmoen, Jan A. S. Bremnes, Stig Tore Johanessen, Magnus L.
%Kirø, Ola Martin T. Støvneng, and Håvard Tørresen, \textit{IEEE HeterWMN 2012, Anaheim,
%CA, USA, 3 December 2012}

\item Johnsen, Frank T., Trude H. Bloebaum, J. H. Nordmoen, Jan AS Bremnes,
Stig Tore Johanessen, Magnus L. Kiro, Ola Martin T. Stovneng, and Havard
Torresen. "Role-based Quality of Service for Web services." 
In Globecom Workshops (GC Wkshps), 2012 IEEE, pp. 453-458. IEEE, 2012.

\end{itemize}

\section*{Certificates, Courses and other Distinctions}
\begin{itemize}
    \item[14.02.2014 :] 1. place in the European BEST Engineering competition, Case
Study. 

	\item[04.05.2013 :] Basic Sailing course. 

    \item[07.02.2012 :] 6 hour course in accounting and budgeting for volunteer organizations. 

	\item[28.09.2008 :] Jose Silva´s UltraMind ESP System certificate.  

\end{itemize}

% drivers licences etc. 
\section*{Skills}
\begin{itemize}
	\item[Languages]:\\
	Norwegian – Native \\
	English – Good \\
	German – Limited working proficiency

	\item[Drivers Licences]:\\
	Car, class B\\
	Forklift, class T1, T2, T3, T5

	\item[IT and Technical]:\\
	{\bf Advanced:} & Linux(desktop and server), Java, Python, PHP, Perl,
Bash, HTML, CSS, JavaScript, (My)SQL, LaTeX
	
	{\bf Good:} & Git, Xml, Spring framework, Flask, D3, Agile development methodologies,
Academic writing, 
\end{itemize}

\section*{References:}
\begin{itemize}
    \item[Academic Work :] \textit{Lars Pettersen} - Consultant Manager 
	\\(+47) 480 86 946, lars.pettersen@academicwork.no

    \item[FFI :] \textit{Dr. Frank T. Johnsen} - Senior Researcher
	\\(+47) 916 05 904, Frank-Trethan.Johnsen@ffi.no

    \item[iNic :] \textit{Hans Petter Sommersen} - General Manager
	\\(+47) 916 95 000, hp@sommersen.no

%    \item[Proffcom :] \textit{Birgit Ohlsen} - Manager of Customer Service 
%	\\(+47) 959 82 577, Birgith.Olsen@proffcom.no 
\end{itemize}

%\subsection*{Proceedings}
%\begin{itemize}
%\item A generalized T-Test and measure of multivariate dispersion,
%  Proc. Second Berkeley Symposium of Mathematical Statistics and
%  Probability, 1951.
%\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}} Written with \LaTeX
  \end{footnotesize}
\end{center}

\end{document}
